% Chapter 1
\chapter*{Acknowledgement}
\hspace{5mm}I would like to thank Prof. Sachin Patkar and Mr. Vinay b. Y. Kumar, PhD Student of Electrical Engineering IIT Bombay of Electrical Engineering Department, IIT Bombay for his continuous guidance and support throughout my M-Tech Project. The idea and work is based on Mr. Yatish Turakhia's Dual Degree project. Yatish did his DDP under the guidance of Prof. Patkar and his project work and report helped me providing the core idea from his research work, valuable attention, and suggestions and troubleshooting. I want to extend my special thanks to Shaishav, Mandar Datar (PhD students in HPC Lab), Sandeep Rasoori (project staff in HPC Lab) and Shubrata Sharma (project staff in HPC Lab), Electrical Engineering, IIT Bombay for their help and support to understand software tools or algorithms. HPC Lab has been the excellent workplace for me. I wish to acknowledge the contribution of HPC Lab to provide the most of the resources needed for my M-Tech Project. I want to thank all the HPC Lab members and all of my friends for their precious support. I want to share my thanks to Michael K. Papamichael, Carnegie Mellon University to allow us to use CONNECT - NoC RTL for my specification. I would like to acknowledge VLSI Design Lab, Electrical Engineering, and IIT Bombay for allowing me to use their software licenses. I would also like to acknowledge and thank Wadhwani Electronics Lab for their kind support and help time to time and also Ministry of HRD, Government of India for funding my Master’s degree. I am very grateful to my parents for their blessing, encouragement and support to work.
